

\documentclass[12]{article}
\begin{document}
\begin{titlepage}
\begin{center}
\huge{\bfseries A report about my experience as head girl at Maryhill high school}\\
\end{center}
\begin{flushright}
\textsc{\large NAKIGANDA ANGELLA\\
RESEARCH METHODOLOGY\\
14/U/11371/PS
214004032
}
\end{flushright}
\end{titlepage}
\section{Introduction}
I was entrusted the office of the Head girl Maryhill High School on 17th June 2012
 A lot happened during that period, some achievements, challenges and possible solutions that overcame them.
\section{Achievements}
I conducted weekend roll calls with the help of other prefects. This helped us monitor students’ attendance and presence in school over the weekends which had faded out by the regime which handed over to us.
Class captains’ rights were fully advocated for and formed an association for captains, “Class Captain Association” (CCA) which consisted of forty four members.
I launched a campaign purposed to fight vulgar language, a habit that was strongly rooted in most of our fellow students in all classes currently glad that the vice has reduced.
I organized several classroom inspections in conjunction with the compound and sanitary departments which were aimed at maintaining a convenient classroom environment. The best classes were rewarded with sodas from our administration and the worst two would serve in a weekend communal work before being roll called as a penalty for their failure to keep to the standards of the school
The library was moped regularly by different classes from form one to form three and a duty Rota was designed for this program.
Sometimes, questionnaires were designed and we used them to represent students’ views to the administration.
\section{Challenges}

Insufficient supply of brooms which made the class captains’ work hard.
Recognition of class captains as grass root leaders was still lacking and the respect given to them was also low and also class captains’ tags were lost by the previous captains and therefore only recognized at class level.

Some students naturally had a disrespectful character towards prefects and also due to the fact that leaders are always hated, I could not satisfies every student’s needs

I had to try my best to be exemplary which was quiet challenging
\section{Appreciation}
Special thanks go out to entire community of Maryhill high school for such a great opportunity especially those that cooperated with me because it was such a great experience from where I learned a lot.

\section{Conclusion}.

I pray that this institution shall forever stand firm, grow from strength to strength, continue being a school of Joy and pride and nurturing Uganda’s future generation.
\end{document}

